\emph{Light Exposure Behavior Assessment (LEBA)}: Long and Short Form

### 2021-10-16 manuscript.Rmd
Added gt table

documentclass     : "apa6"
classoption       : "man"
output            : 
  papaja::apa6_pdf:
    latex_engine: xelatex
mainfont: Arial
---

@@

install.packages("devtools")
install.packages("semTools")
install.packages("MOTE")
install.packages("psych")
install.packages("dlookr")
install.packages("tidyverse")
install.packages("qgraph")
install.packages("kableExtra")
install.packages("paran")
install.packages("EFA.MRFA")
install.packages("rsvg")
install.packages("ggcorrplot")
install.packages("car")
install.packages("semTable")
install.packages("magick")
install.packages("mirt")
install.packages("cowplot")
devtools::install_github('rich-iannone/DiagrammeR')
devtools::install_github("crsh/papaja", force = T)
install.packages("DiagrammeRsvg")
devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
devtools::install_github("crsh/citr")
remotes::install_github("jthomasmock/gtExtras")
install.packages("gt")
install.packages("plyr")
```

@@

library(papaja) # devtools::install_github("crsh/papaja")
library(lavaan)
library(semPlot) #devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
library(semTools)
library(MOTE)
library(psych)
library(dlookr)
library(plyr)
library(tidyverse)
library(qgraph)
library(kableExtra)
library(paran) # Parallel analysis
library(EFA.MRFA) # Hull method
library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
library(DiagrammeRsvg) #For DiagrammeR
library(rsvg) #For DiagrammeR
library(ggcorrplot)
library(car) #Reversecoding
library(semTable)
library(magick)
library(mirt)
library(gtsummary)
r_refs("references.bib")
```

@@

+-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+
| Name                                            | Authors | Translations | Description                                                                            | Relevant Items |
+=================================================+=========+==============+========================================================================================+================+
| Visual Light Sensitivity Questionnaire-8        |         |              | Eight-question survey to assess the presence and severity of photosensitivity symptoms |                |
+-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+
| Office Light Survey                             |         |              | To assess electrical lighting environment in Office                                    |                |
+-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+
| Harvard Light Exposure Assessment Questionnaire |         |              | Self-administered semiquantitative light questionnaire                                 |                |
+-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+
| Hospital Lighting Survey                        |         |              | 23 items questionnaire to assess light environment in a hospital                       |                |
+-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+
| Morningness-Eveningness Questionnaire           |         |              | 19 items questionnaire to understand your body clock                                   |                |
+-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+
| Munich Chronotype Questionnaire (MCTQ)          |         |              | 17 items questionnaire to understand individuals phase of entrainment                  |                |
+-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+
| Assessment of Sleep Environment                 |         |              | 13 items questionnaire measuring your sleep environment quality                        |                |
+-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+
| The Pittsburgh Sleep Quality Index (PSQI)       |         |              | 9 items inventory to measure sleep quality and sleeping pattern                        |                |
+-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+

@@

+-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+

@@

@@

```{r figCor,out.width="70%",out.width="100%",fig.cap= "Correlation plot of the items",results='asis', fig.align='center'}

@@

```{r facIdFig, fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot (C) Hull Method',  warning=FALSE}
cowplot::plot_grid(parallel, scree.plot,Hull, labels = c('(A)', '(B)', '(C)'), label_size = 8)

@@

@@

### CFA Data
CFA.data <- sem.data[429:690,]
CFARitem8 = recode(CFA.data$item8, '1=5; 2=4; 3=3; 4=2; 5=1')
CFARitem37 = recode(CFA.data$item37, '1=5; 2=4; 3=3; 4=2; 5=1')
CFARitem26 = recode(CFA.data$item26, '1=5; 2=4; 3=3; 4=2; 5=1')
CFA.data <- CFA.data %>% 
  mutate(Ritem8 = CFARitem8, Ritem37 = CFARitem37, Ritem26 = CFARitem26)

@@

```{r IRT data, include=FALSE}

IRTitem8 = recode(sem.data$item8, '1=5; 2=4; 3=3; 4=2; 5=1')
IRTitem37 = recode(sem.data$item37, '1=5; 2=4; 3=3; 4=2; 5=1')
IRTitem26 = recode(sem.data$item26, '1=5; 2=4; 3=3; 4=2; 5=1')
sem.data <- sem.data %>% 
  mutate(Ritem8 = IRTitem8, Ritem37 = IRTitem37, Ritem26 = IRTitem26)

@@

# Plots ####
## F1 Plots ####
F1_OCC <- plot(F1_fit, type = "trace", facet =T, main = "Blue Filter OCC")
F1_info <- plot(F1_fit, type = "infoSE", main = "Blue Filter Test Information")
F1_iteminfo <- plot(F1_fit, type = "infotrace", 
                    facet_items = T, main = "Blue Filter")

## F2 Plots ####
F2_OCC <- plot(F2_fit, type = "trace", facet =T, main = "Natural Light OCC")
F2_info <- plot(F2_fit, type = "infoSE", main = "Natural Light Test Information")
F2_iteminfo <- plot(F2_fit, type = "infotrace", facet_items = T, main = "Natural Light")

## F3 Plots ####
F3_OCC <-plot(F3_fit, type = "trace", facet =T, main = "Smart Device OCC")
F3_info <- plot(F3_fit, type = "infoSE", main = "Smart Device Test Information")
F3_iteminfo <- plot(F3_fit, type = "infotrace", 
                    facet_items = T, main = "Smart Device")

## F4 Plots ####
F4_OCC <-plot(F4_fit, type = "trace", facet =T, main = "Sleep Environment OCC")
F4_info <- plot(F4_fit, type = "infoSE", main = "Sleep Environment Test Information")
F4_iteminfo <- plot(F4_fit, type = "infotrace", facet_items = T,main = "Sleep Environment")

## F5 Plots ####
F5_OCC <-plot(F5_fit, type = "trace", facet =T, main = "Electric Light OCC")
F5_info <- plot(F5_fit, type = "infoSE", main = "Electric Light Test Information")
F5_iteminfo <- plot(F5_fit, type = "infotrace", facet_items = T,main = "Electric Light")

@@

F1_info <- plot(F1_fit, type = "infoSE", main = "Blue Filter")

F2_info.redu <- plot(F2_fit.redu, type = "infoSE", main = "Natural Light Test Information")

F3_info.redu <- plot(F3_fit.redu, type = "infoSE", main = "Smart Device Test Information")

F4_info.redu <- plot(F4_fit.redu, type = "infoSE", main = "Sleep Environment Test Information")

F5_info <- plot(F5_fit, type = "infoSE", main = "Electric Light Test Information")

@@

>>>>

documentclass     : "apa6"
classoption       : "man"
output            : 
  papaja::apa6_pdf:
    latex_engine: xelatex
mainfont: Helvetica
---

@@

install.packages("devtools")
install.packages("semTools")
install.packages("MOTE")
install.packages("psych")
install.packages("dlookr")
install.packages("tidyverse")
install.packages("qgraph")
install.packages("kableExtra")
install.packages("paran")
install.packages("EFA.MRFA")
install.packages("rsvg")
install.packages("ggcorrplot")
install.packages("semTable")
install.packages("magick")
install.packages("mirt")
install.packages("cowplot")
devtools::install_github('rich-iannone/DiagrammeR')
devtools::install_github("crsh/papaja", force = T)
install.packages("DiagrammeRsvg")
devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
devtools::install_github("crsh/citr")
remotes::install_github("jthomasmock/gtExtras")
install.packages("gt")
remotes::install_github("jthomasmock/gtExtras")
install.packages("questionr")
devtools::install_github("lbusett/insert_table")
```

@@

library(papaja) # devtools::install_github("crsh/papaja")
library(lavaan)
library(semPlot) #devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
library(semTools)
library(MOTE)
library(car)#revercoding 
library(psych)
library(dlookr)
library(plyr)
library(tidyverse)
library(qgraph)
library(kableExtra)
library(paran) # Parallel analysis
library(EFA.MRFA) # Hull method
library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
library(DiagrammeRsvg) #For DiagrammeR
library(rsvg) #For DiagrammeR
library(ggcorrplot)
library(semTable)
library(magick)
library(mirt)
library(gtsummary)
library(gt)
library(gtExtras)
library(likert)
library(kutils)
r_refs("references.bib")
```

@@

```{=html}
<!-- -->
```
    \newpage
    \begin{landscape}

+-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+
| Name                                            | Authors | Description                                                                            | Relevant Items | Adaptations |
+=================================================+=========+========================================================================================+:==============:+=============+
| Visual Light Sensitivity Questionnaire-8        | a       | Eight-question survey to assess the presence and severity of photosensitivity symptoms | all            | jhghjgjhgfd |
+-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+
| Office Light Survey                             | b       | Multi-item questionnaire to assess electrical lighting environment in office           | aa             | gh          |
+-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+
| Harvard Light Exposure Assessment Questionnaire | c       | Self-administered semiquantitative light qestionnaire                                  | aa             | as          |
+-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+
| Hospital Lighting Survey                        | d       | 23 items questionnaire to assess light environment in a hospital                       | dd             | fg          |
+-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+
| Morningness-Eveningness Questionnaire           | e       | 19 items questionnaire to understand your body clock                                   | ff             | hj          |
+-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+
| Munich Chronotype Questionnaire (MCTQ)          | f       | 17 items questionnaire to understand individuals phase of entrainment                  | ff             | jk          |
+-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+
| Assessment of Sleep Environment                 | g       | 13 items questionnaire measuring your sleep environment quality                        | ff             | kl          |
+-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+
| The Pittsburgh Sleep Quality Index (PSQI)       | h       | 9 items inventory to measure sleep quality and sleeping pattern                        | ff             | klfrgfgvfg  |
+-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+

@@

+-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+

@@

    \end{landscape}

@@

```{r figCor,out.width="100%",fig.cap= "Correlation plot of the items",results='asis', fig.align='center'}

@@

```{r facIdFig, out.height="100%", out.width="200%",fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot (C) Hull Method',  warning=FALSE}
cowplot::plot_grid(parallel, scree.plot,Hull, labels = c('(A)', '(B)', '(C)'), label_size = 8)

@@

```{r gtvis, include =F}
## Recoding sem.data$item8
gt.data <- sem.data
gt.data$item8 <- as.character(gt.data$item8)
gt.data$item8 <- fct_recode(gt.data$item8,
  "5" = "1",
  "4" = "2",
  "2" = "4",
  "1" = "5"
)

## Recoding gt.data$item26
gt.data$item26 <- as.character(gt.data$item26)
gt.data$item26 <- fct_recode(gt.data$item26,
  "5" = "1",
  "4" = "2",
  "2" = "4",
  "1" = "5"
)
## Recoding gt.data$item37
gt.data$item37 <- as.character(gt.data$item26)
gt.data$item37 <- fct_recode(gt.data$item26,
  "5" = "1",
  "4" = "2",
  "2" = "4",
  "1" = "5"
)

names(gt.data)[names(gt.data) == "item1"] <- "item01"
names(gt.data)[names(gt.data) == "item3"] <- "item03"
names(gt.data)[names(gt.data) == "item4"] <- "item04"
names(gt.data)[names(gt.data) == "item7"] <- "item07"
names(gt.data)[names(gt.data) == "item8"] <- "item08"
names(gt.data)[names(gt.data) == "item9"] <- "item09"

#EFA data
gt.efa.data <- gt.data[1:428, ]

gt.efa.data.table <- gt.efa.data %>% 
  dplyr::select(item16, item36, item17,
                 item11, item10,item12,item07,item08,item09,
                 item27,  item03, item40,  item30, item41,
                 item33, item32,item35, item37,item38, 
                 item46, item45, item25, item04, item01,item26)

#Creating long data
gt.efa.long <- as.data.frame(gather(gt.efa.data.table, Items, value))
gt.efa.long$value <- as.numeric(as.character(gt.efa.long$value))

#Summarizing and creating gt object
gt.efa.tab <- gt.efa.long %>% 
  group_by(Items) %>% 
  # calculate summary stats & create data for the histogram and density plot
  dplyr::summarise(
    nr = n(),
    mean = mean(value, na.rm = TRUE),
    med = median(value, na.rm = TRUE),
    sd = sd(value, na.rm = TRUE),
    hist_data = list(value),
    dens_data = list(value),
    .groups = "drop"
  ) %>% 
  gt()

#Preparation for likert data
efa.LEBA.likert <- as.data.frame(gt.efa.data.table)

recod_LEBA <- c( "1" = "Never", "2" = "Rarely", "3"= "Sometimes","4" = "Often",
                 "5" = "Always")
efa.LEBA.likert <-  mutate(efa.LEBA.likert, across(starts_with("item"), ~unname(recod_LEBA[.])))

efa.LEBA.Factor = as.data.frame(lapply(efa.LEBA.likert,factor,
                                   ordered = T))
#get the items name
efa.items <- names(efa.LEBA.Factor) 
#Calculate percentage
efa.percentage <- kutils::likert(efa.LEBA.Factor, vlist = efa.items )

efa.percentage <- efa.percentage$table %>% 
  as.data.frame(.)

#data wrangling
labels <- c("Always", "Never","Often", "Rarely", "Sometimes","Total")
as.data.frame(labels)

full.efa.percentage <- cbind(labels,efa.percentage) #tables with labels  
full.efa.percentage<- t(full.efa.percentage ) #transpose
as.data.frame(full.efa.percentage)
full.efa.percentage1 <- full.efa.percentage[-1,-6] #removing 1st row and total column
full.efa.percentage2 <- full.efa.percentage1[, c(2, 4, 5, 3,1)]# rearranging
as.data.frame(full.efa.percentage2)

colnames(full.efa.percentage2) <- c("Never","Rarely","Sometimes","Often","Always")

efa.Items <- rownames(full.efa.percentage2)
as.data.frame(efa.Items)
full.efa.percentage3 <- cbind(efa.Items,full.efa.percentage2)

full.efa.percentage3 <- full.efa.percentage3[order(efa.Items),] 
full.efa.percentage3 <- as.data.frame(full.efa.percentage3[,-1]) %>% 
  gt()

gt.efa.table <- gt.efa.tab$'_data'
gt.liket.efa <- full.efa.percentage3$"_data"

efaTable <-  cbind( gt.efa.table, gt.liket.efa)%>% 
  gt()

gt.cfa.data <- gt.data[429:690,]
gt.cfa.data.table <- gt.cfa.data %>% 
  dplyr::select(item16, item36, item17,
                 item11, item10,item12,item07,item08,item09,
                 item27,  item03, item40,  item30, item41,
                 item32,item35,item38, item33, 
                 item46, item45, item25, item04, item01 )

gt.cfa.long <- gather(gt.cfa.data.table, Items, value)
gt.cfa.long$value <- as.numeric(as.character(gt.cfa.long$value))
gt.cfa.tab <- gt.cfa.long %>% 
  group_by(Items) %>% 
# calculate summary stats & create data for the histogram and density plot
  summarise(
    nr = n(),
    mean = mean(value, na.rm = TRUE),
    med = median(value, na.rm = TRUE),
    sd = sd(value, na.rm = TRUE),
    hist_data = list(value),
    dens_data = list(value),
    .groups = "drop"
  ) %>%

  gt()

#Preparation for likert data
cfa.LEBA.likert <- as.data.frame(gt.cfa.data.table)

recod_LEBA <- c( "1" = "Never", "2" = "Rarely", "3"= "Sometimes","4" = "Often",
                 "5" = "Always")
cfa.LEBA.likert <-  mutate(cfa.LEBA.likert, across(starts_with("item"), ~unname(recod_LEBA[.])))

cfa.LEBA.Factor = as.data.frame(lapply(cfa.LEBA.likert,factor,
                                   ordered = T))
#get the items name
cfa.items <- names(cfa.LEBA.Factor) 
#Calculate percentage
cfa.percentage <- kutils::likert(cfa.LEBA.Factor, vlist = cfa.items )

cfa.percentage <- cfa.percentage$table %>% 
  as.data.frame(.)

#data wrangling
labels <- c("Always", "Never","Often", "Rarely", "Sometimes","Total")
as.data.frame(labels)

full.cfa.percentage <- cbind(labels,cfa.percentage) #tables with labels  
full.cfa.percentage <- t(full.cfa.percentage ) #transpose
as.data.frame(full.cfa.percentage)
full.cfa.percentage1 <- full.cfa.percentage[-1,-6] #removing 1st row and total column
full.cfa.percentage2 <- full.cfa.percentage1[, c(2, 4, 5, 3,1)]# rearranging
as.data.frame(full.cfa.percentage2)

colnames(full.cfa.percentage2) <- c("Never","Rarely","Sometimes","Often","Always")

cfa.Items <- rownames(full.cfa.percentage2)
as.data.frame(cfa.Items)
full.cfa.percentage3 <- cbind(cfa.Items,full.cfa.percentage2)

full.cfa.percentage3 <- full.cfa.percentage3[order(cfa.Items),] 
full.cfa.percentage3 <- as.data.frame(full.cfa.percentage3[,-1]) %>% 
  gt()

gt.cfa.table <- gt.cfa.tab$'_data'
gt.liket.cfa <- full.cfa.percentage3$"_data"

cfaTable <-  cbind( gt.cfa.table, gt.liket.cfa) %>% 
  gt()

efa.gt <- efaTable$"_data"
cfa.gt <- cfaTable$"_data"

gt.fullTable <-  rbind( efa.gt, cfa.gt) %>% 
  gt() %>% 
# histogram and density plots
  gtExtras::gt_sparkline(
    hist_data,
    type = "histogram",
    line_color = "black", 
    fill_color = "grey",
    bw = 1,
    same_limit = TRUE)%>%
  gtExtras::gt_sparkline(
    dens_data,
    type = "density",
    line_color = "black", 
    fill_color = "grey",
    bw = 0.75,
    same_limit = TRUE
  )%>%
# format decimals
  fmt_number(columns = mean:sd, decimals = 1) %>%
# header
  tab_header(
    title = md("**LEBA**"),
    subtitle = md("Summary results of LEBA (N =690)")
  ) %>% 
  tab_footnote(
    footnote = md("**Histogram**"),
    locations = cells_column_labels(columns = hist_data)
  ) %>%
  tab_footnote(
    footnote = md("**Density**"),
    locations = cells_column_labels(columns = dens_data)
  ) %>% 
#create groups of columns
tab_spanner(
  label = "Items",
  columns = Items
) %>%
  tab_spanner(
    label = "Summary Statistics",
    columns = nr:sd
  ) %>%
  tab_spanner(
    label = "Graphics",
    columns = hist_data:dens_data
  ) %>% 
  tab_spanner(
    label = "Response Pattern",
    columns = Never:Always
  ) %>%
# change column names to appear in the table
cols_label(
  Items = ("LEBA  Items"),
  nr = ("n"),
  mean = ("Mean"),
  med = ("Median "),
  sd = (("SD")),
  hist_data = "Histogram",
  dens_data = "Density"
) %>%
# set alignment as per wish
  cols_align(
    align = "center",
    columns = everything()
  ) %>%
  opt_align_table_header(align = "left") %>%
# add coloured dots and lines on the first column
  gt_plt_dot(
    mean,
    Items,
    palette = "ggthemes::fivethirtyeight"
  ) %>% 
    tab_row_group(
      group = "CFA (n =262)",
     rows = 26:48

  ) %>% 
  tab_row_group(
  group = "EFA (n = 428)",
    rows = 1:25  
  ) %>% gtsave("Manuscript.figures/gt.png")

```{r gtPic, echo=FALSE, out.height="100%", out.width="200%", results= 'asis'}
knitr::include_graphics('Manuscript.figures/gt.png')

@@

### CFA Data
CFA.data <- sem.data[429:690,]

## Recoding CFA.data$item8 into CFA.data$Ritem8
CFA.data$Ritem8 <- as.character(CFA.data$item8)
CFA.data$Ritem8 <- fct_recode(CFA.data$Ritem8,
  "5" = "1",
  "4" = "2",
  "2" = "4",
  "1" = "5"
)
CFA.data$Ritem8 <- as.numeric(as.character(CFA.data$Ritem8))

## Recoding CFA.data$item37 into CFA.data$item37_rec
CFA.data$Ritem37 <- as.character(CFA.data$item37)
CFA.data$Ritem37 <- fct_recode(CFA.data$Ritem37,
  "5" = "1",
  "4" = "2",
  "2" = "4",
  "1" = "5"
)
CFA.data$Ritem37 <- as.numeric(as.character(CFA.data$Ritem37))

## Recoding CFA.data$item26 into CFA.data$Ritem26
CFA.data$Ritem26 <- as.character(CFA.data$item26)
CFA.data$Ritem26 <- fct_recode(CFA.data$Ritem26,
  "5" = "1",
  "4" = "2",
  "2" = "4",
  "1" = "5"
)

@@

```{r IRT data, include=FALSE}
## Recoding sem.data$item8 into sem.data$Ritem8
sem.data$Ritem8 <- as.character(sem.data$item8)
sem.data$Ritem8 <- fct_recode(sem.data$Ritem8,
  "5" = "1",
  "4" = "2",
  "2" = "4",
  "1" = "5"
)
sem.data$Ritem8 <- as.numeric(as.character(sem.data$Ritem8))
# Recoding sem.data$item26 
sem.data$Ritem26 <- as.character(sem.data$item26)
sem.data$Ritem26 <- fct_recode(sem.data$Ritem26,
  "5" = "1",
  "4" = "2",
  "2" = "4",
  "1" = "5"
)
sem.data$Ritem26 <- as.numeric(as.character(sem.data$Ritem26))

# Recoding sem.data$item37 i
sem.data$Ritem37 <- as.character(sem.data$item37)
sem.data$Ritem37 <- fct_recode(sem.data$Ritem37,
  "5" = "1",
  "4" = "2",
  "2" = "4",
  "1" = "5"
)
sem.data$Ritem37 <- as.numeric(as.character(sem.data$Ritem37))

@@

# Plots ####
## F1 Plots ####
F1_OCC <- plot(F1_fit, type = "trace", facet =T, main = "Blue Filter OCC")
F1_info <- plot(F1_fit, type = "infoSE", main = "F1")
F1_iteminfo <- plot(F1_fit, type = "infotrace", 
                    facet_items = T, main = "Blue Filter")

## F2 Plots ####
F2_OCC <- plot(F2_fit, type = "trace", facet =T, main = "Natural Light OCC")
F2_info <- plot(F2_fit, type = "infoSE", main = "F2")
F2_iteminfo <- plot(F2_fit, type = "infotrace", facet_items = T, main = "Natural Light")

## F3 Plots ####
F3_OCC <-plot(F3_fit, type = "trace", facet =T, main = "Smart Device OCC")
F3_info <- plot(F3_fit, type = "infoSE", main = "F3")
F3_iteminfo <- plot(F3_fit, type = "infotrace", 
                    facet_items = T, main = "Smart Device")

## F4 Plots ####
F4_OCC <-plot(F4_fit, type = "trace", facet =T, main = "Sleep Environment OCC")
F4_info <- plot(F4_fit, type = "infoSE", main = "F4")
F4_iteminfo <- plot(F4_fit, type = "infotrace", facet_items = T,main = "Sleep Environment")

## F5 Plots ####
F5_OCC <-plot(F5_fit, type = "trace", facet =T, main = "Electric Light OCC")
F5_info <- plot(F5_fit, type = "infoSE", main = "F5")
F5_iteminfo <- plot(F5_fit, type = "infotrace", facet_items = T,main = "Electric Light")

@@

F1_info <- plot(F1_fit, type = "infoSE", main = "F1")

F2_info.redu <- plot(F2_fit.redu, type = "infoSE", main = "F2")

F3_info.redu <- plot(F3_fit.redu, type = "infoSE", main = "F3")

F4_info.redu <- plot(F4_fit.redu, type = "infoSE", main = "F4")

F5_info <- plot(F5_fit, type = "infoSE", main = "F5")

@@

```{r itminfo, fig.cap="Item information curves (A) blue filter (B) natural light (C)smart device (D)sleep environment (E)electic light", warning=FALSE, out.width="100%", out.height="120%"}
plot_grid(F1_info, F2_info.redu,F3_info.redu,F4_info.redu,F5_info, 
          labels = c('A', 'B','C', 'D', 'E' ), label_size = 10)
